---
title: "Homework-9"
author: "Anthony Yang"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", fig.height=3, fig.width=6, warning=FALSE, message=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=100))

solder <- read.csv('solder.csv')
turnout <- read.csv('turnout.csv')

suppressWarnings({
  suppressPackageStartupMessages(library(ggplot2))
  suppressPackageStartupMessages(library(tidyverse))
  suppressPackageStartupMessages(library(dplyr))
  suppressPackageStartupMessages(library(mosaic)) 
  suppressPackageStartupMessages(library(effectsize))
  suppressPackageStartupMessages(library(MatchIt))
})
```

Link to GitHub Repository: https://github.com/anthonyangg/sds315-Homework9/tree/main

## Problem 1

#### Part A

```{r echo = FALSE}
group1998 <- filter(turnout, voted1998=='1')
gotv_Yes <- prop(group1998$GOTV_call == '1')
gotv_No <- prop(group1998$GOTV_call == '0')

diffvoting <- do(5000) * diffprop(voted1998=='1'~GOTV_call, data=resample(turnout))

confint(diffvoting, level = 0.95)
```


The proportion of people who received a GOTV call given that they voted in 1998 is `r gotv_Yes` and the proportion of those who didn't is `r gotv_No`. When examining the resampled data of the proportion of people who voted in 1998 for those who received GOTV calls and those who didn't, the difference in proportion is between 0.144 and 0.261 at a 95% level of confidence. Based on this we can determine GOTV call recipients are 14.4% to 26.1% more likely to have voted in 1998 than those who didn't receive a GOTV call. 

#### Part B

```{r echo=FALSE}
lm0 = lm(formula = voted1998 ~ GOTV_call, data = group1998)
coef(lm0)

lm1 = lm(formula = voted1998 ~ GOTV_call + voted1996 + AGE + MAJORPTY, data = group1998)
coef(lm1)

ggplot(turnout) + geom_col(aes(x=GOTV_call, y=voted1998)) + facet_wrap(~voted1996) +
  xlab('GOTV Call Recipients (Yes/No)') + ylab("Number of Voters in 1998") +
  ggtitle("Number of voters in 1998 based on GOTV Call Recipients based on 1996 Election") + theme_classic()

ggplot(turnout) + geom_col(aes(x=GOTV_call, y=voted1998)) + facet_wrap(~MAJORPTY) +
  xlab('GOTV Call Recipients (Yes/No)') + ylab("Number of Voters in 1998") +
  ggtitle("Number of voters in 1998 based on GOTV Call Recipients based on Majority") +
  theme_classic()

turnout <- mutate(turnout, AGE_GROUP = round(AGE, digits = -1))

ggplot(turnout) + geom_col(aes(x=GOTV_call, y=voted1998)) + facet_wrap(~AGE_GROUP) +
  xlab("GOTV Call Recipients (Yes/No)") + ylab("Number of Voters in 1998") +
  ggtitle("Number of voters in 1998 based on GOTV Call Recipients based on Age") +
  theme_classic()
```


#### Part C

```{r echo=FALSE}
match_data = matchit(GOTV_call ~ voted1996 + AGE + MAJORPTY, data = turnout, ratio = 5)
summary(match_data)

matched_data = match.data(match_data)

mean(AGE ~ GOTV_call, data = matched_data)

xtabs(~voted1996 + GOTV_call, data=matched_data) %>%
  prop.table(margin=2)

xtabs(~MAJORPTY + GOTV_call, data = matched_data) %>%
  prop.table(margin = 2)

data <- filter(matched_data, voted1998 == '1')

gotvYes <- prop(data$GOTV_call == '1')
gotvNo <- prop(data$GOTV_call == '0')

diffvoting <- do(5000) * diffprop(voted1998=='1'~GOTV_call, data=resample(matched_data))

confint(diffvoting, level = 0.95)
```

The proportion of people who received a GOTV call given that they voted in 1998 is `r gotvYes` and the proportion of those who didn't is `r gotvNo`. When examining the resampled data from the matched dataset after balancing all the confounding variables of the proportion of people who voted in 1998 for those who received GOTV calls and those who didn't, the difference in proportion is between 0.0066 and 0.1377 at a 95% level of confidence. Based on this we can determine GOTV call recipients are 0.66% to 13.77% more likely to have voted in 1998 than those who didn't receive a GOTV call. 


## Problem 2

#### Part A

```{r echo=FALSE}
ggplot(solder) + geom_col(aes(x=Opening, y = skips)) + 
  xlab("Size Opening of Solder Gun") + ylab("Number of Skips") +
  labs(title = "Number of Skips per Opening size of Solder Gun", tag = 'Figure 1') + 
  theme_classic()

ggplot(solder) + geom_col(aes(x=Solder, y = skips)) + 
  xlab("Alloy Thickness") + ylab("Number of Skips") +
  labs(title = "Number of Skips for Alloy Thickness", tag = 'Figure 2') + 
  theme_classic()
```

Figure 1 shows the number of skips for each type of opening of the solder gun. From the graph, we can see the trend that as the opening size of the gun decreases, the number of skips increases drastically. In fact, the number of skips for a small size opening is well over 3000 skips while the number of skips for the large size opening is not even 500 skips. 

Figure 2 shows the number of skips for each thickness of alloy. We can see that the thin alloy has many more skips than a thick alloy. We can determine the relationship that thinner alloys have more skips. 

#### Part B

```{r echo=FALSE}
lm0 = lm(skips ~ Opening, data = solder)
coef(lm0)

lm1 = lm(skips ~ Solder, data = solder)
coef(lm1)

lm2 = lm(skips ~ Opening + Solder + Opening:Solder, data=solder)
coef(lm2)

confint(lm2, level = 0.95)

eta_squared(lm2, partial = FALSE)
```


#### Part C


First we started with a model for number of skips that has only the Solder Gun Opening Size variable in it. The R-squared value of this model is 0.26 meaning the Opening Size variable accounts for 26% of the total variation in the number of skips on the circuit board. Next, we we added the soldering alloy thickness to the model, so now we have skip ~ Opening + Solder. With a R-squared value
is 0.10, Alloy Thickness accounts for 10% of the total variation in the number of skips.
Finally, we add the interaction, giving us the model skips ~ Opening + Solder + Opening:Solder. The R-squared value is 0.08. Thus any interaction or “synergy” effects between the Opening and Solder variables account for about 8% of the overall variation in number of skips.

#### Part D


In order to minimize the number of skip in the manufacturing process, I recommend the a large opening size of the solder gun and a thick alloy because the opening size, alloy thickness, and their interaction account for 44% of variation in the number of skips in the manufacturing process so it's crucial to control these variables. Additionally, when looking at the two figures above, it shows that a large opening and a thick alloy had the least number of skips. 
